Trends of downward SDR in Thessaloniki

### 2023-05-10 Article.Rmd
Commit 2023-05-10 08:17

output:  
  bookdown::pdf_document2:
    number_sections: no
    fig_caption:     yes
    keep_tex:        no
    latex_engine:    xelatex
    toc:             yes
    toc_depth:       4
    fig_width:       7
    fig_height:      4.5
  html_document:
    toc:             true
    fig_width:       7.5
    fig_height:      5

@@

<!-- time span -->
The global radiation was obtained from the pyranometer CM-21, for the period from
`r min(ALL_1_daily_DESEAS$Date)` to `r max(ALL_1_daily_DESEAS$Date)`.
In some algorithms we auxialiary used direct radiation data for comparisons, obtained by a CM-21 pyrheliometer, with data span from 
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])` to `r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.

@@

<!-- measurement -->
The signal of the CM-21 pyranometer is sampled with a rate of $1 {Hz}$, and a record the average signal and the standard deviation every one minute is recorded.
<!-- dark correction -->
The measurements are corrected for the zero offset of the instrument, using the "dark signal" (Sun elevation angle bellow $-10^\circ$, for a period of $3 h$).
<!-- physical quantities -->
The signal is converted to radiation using a ramped value of the instrument sensitivity, derived from the eight laboratory calibrations of the instrument, during the study period.

@@

```{r trendALL, echo=F, fig.cap="Daily Global radiation seasonal anomaly and long term trend, for all sky conditions."}
knitr::include_graphics("./images/LongtermTrends-2.pdf")
```

@@

Similar we have produced the deseaonilised trend for different sky conditions for each season of the year, using the corresponding mean monthly values.

@@

<!-- Not showing this trend -->
```{r cumsumCLEAR, echo=F, fig.cap="Donditions.", include=FALSE}
knitr::include_graphics("./images/CumulativeDailyCumSum-5.pdf")
```

@@

Both dataset were aggregate in $1^\circ$ SZA bins by am, pm, am+pm

>>>>

output:  
  bookdown::pdf_document2:
    number_sections: no
    fig_caption:     yes
    keep_tex:        no
    latex_engine:    xelatex
    toc:             yes
    toc_depth:       4
    fig_width:       7
    fig_height:      4.5

@@

<!-- time span -->
The global radiation was obtained from the pyranometer CM-21, for the period from
`r min(ALL_1_daily_DESEAS$Date)` to `r max(ALL_1_daily_DESEAS$Date)`.
In some algorithms we auxiliary used direct radiation data for comparisons, obtained by a CM-21 pyrheliometer, with data span from 
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])` to `r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.

@@

<!-- measurement -->
The signal of the CM-21 pyranometer is sampled with a rate of $1 {Hz}$, and a record the average signal and the standard deviation every one minute is recorded.
<!-- dark correction -->
The measurements were corrected for the zero offset of the instrument, using the "dark signal" (Sun elevation angle bellow $-10^\circ$, for a period of $3 h$).
<!-- physical quantities -->
The signal is converted to radiation using a ramped value of the instrument sensitivity, derived from the eight laboratory calibrations of the instrument, during the study period.

@@

```{r trendALL, echo=F, fig.cap="Anomaly (\\%) of the daily Global radiation relative to climatological values for 1993 - 2022. The straight black line shows the long term trend for All-sky conditions."}
knitr::include_graphics("./images/LongtermTrends-2.pdf")
```

@@

Similar we have produced the deseasonalized trend for different sky conditions for each season of the year, using the corresponding mean monthly values.

@@

<!--
Not showing this trend
```{r cumsumCLEAR, echo=F, fig.cap="Donditions.", include=FALSE}
knitr::include_graphics("./images/CumulativeDailyCumSum-5.pdf")
```
-->

@@

Both datasets were aggregate in $1^\circ$ SZA bins by am, pm, am+pm
